### 2008-12-19 talk/ecoop2009/rainbow.tex
swap promotion and virtuals sections

\section{The Rainbow Interpreter}

The JIT compiler is implemented by running the "Rainbow interpreter", whose
output is a compiled function.

Variables and opcodes are colored:

  - green values are known at compile time, and green operations are executed
    when interpreting the bytecode;

  - red values are not known until runtime; the result of a red operation is a
    piece of machine code that will compute the result at runtime.

The Rainbow bytecode is produced at translation time, when the JIT compiler is
generated.

\cfbolz{XXX I think we should be very careful with the rainbow interp. it is a
total implementation-detail and we should only describe it as little as
possible}

\subsection{Example of Rainbow bytecode and execution}

TODO

\section{Promotion}

@@

Virtual structures still avoid the run-time allocation of most
short-lived objects, even in non-trivial situations.  The following
example shows a typical case.  XXX use TLC example

>>>>

Virtual structures still avoid the run-time allocation of most
short-lived objects, even in non-trivial situations.  The following
example shows a typical case.  The TLC interpreter implements application-level
integers as boxes – instances of an \texttt{IntObject} class with a single
field.

\section{Promotion}
\label{sec:promotion}

@@
